Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-20 writing/DraftExposurePaper/DraftExposurePaper.Rmd
rain lag plot code

# Generate a list of unique study fips (all in the eastern US)
my_fips <- closest_dist$fips
my_fips <- unique(my_fips)
storm_lag <- county_rain(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             rain_limit = 150, dist_limit = 500,
                             days_include = -3:3)
storm_lag <- storm_lag %>%
        mutate(storm_county = paste0(storm_id, "_", fips))
data(rain)
rain_lag <- rain %>%
        mutate(storm_county = paste0(storm_id, "_", fips)) %>%
        filter(storm_county %in% storm_lag$storm_county)
rain_lag_plot <- 
```

>>>>

# Generate a list of unique study fips (all in the eastern US)
my_fips <- closest_dist$fips
my_fips <- unique(my_fips)
storm_lag <- county_rain(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             rain_limit = 150, dist_limit = 500,
                             days_include = -3:3)
storm_lag <- storm_lag %>%
        mutate(storm_county = paste0(storm_id, "_", fips))
data(rain)
rain_lag <- rain %>%
        mutate(storm_county = paste0(storm_id, "_", fips)) %>%
        filter(storm_county %in% storm_lag$storm_county)
rain_lag_plot <- ggplot(rain_lag, aes(x = lag, y = precip, group = storm_county)) +
        geom_line(alpha = 0.2, size = 0.5)
rain_lag_plot
```
